---
title: "Milano Family Pizza"
subtitle: "Dual-Site Revenue Audit + Financial Projection"
date: "June 23, 2026"
author: "Elliyeen Research"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 2
    theme: flatly
    highlight: null
    css: tufte.css
    includes:
      in_header: header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.align = "left", fig.retina = 2, dpi = 150, out.width = "100%"
)
library(ggplot2); library(dplyr); library(tidyr)
library(scales); library(knitr); library(kableExtra); library(ggrepel)

theme_audit <- function(base_size = 12) {
  theme_minimal(base_size = base_size) +
    theme(
      plot.title         = element_text(face = "bold", size = base_size + 1, margin = margin(b = 4)),
      plot.subtitle      = element_text(color = "#555555", size = base_size - 1, margin = margin(b = 12)),
      plot.caption       = element_text(color = "#888888", size = base_size - 3, hjust = 0, margin = margin(t = 8)),
      plot.background    = element_rect(fill = "#fafaf8", color = NA),
      panel.background   = element_rect(fill = "#fafaf8", color = NA),
      panel.grid.major.y = element_line(color = "#e8e8e4", linewidth = 0.3),
      panel.grid.major.x = element_blank(),
      panel.grid.minor   = element_blank(),
      axis.line.x        = element_line(color = "#cccccc", linewidth = 0.4),
      axis.line.y        = element_blank(),
      axis.ticks         = element_blank(),
      axis.title         = element_text(size = base_size - 1, color = "#555555"),
      axis.text          = element_text(size = base_size - 1, color = "#333333"),
      legend.position    = "none",
      strip.text         = element_text(face = "bold", size = base_size - 1),
      strip.background   = element_rect(fill = "#f0efea", color = NA)
    )
}

CLR_MAIN  <- "#1f3a3a"
CLR_WEAK  <- "#a05c3c"
CLR_GOOD  <- "#2d6a4f"
CLR_MID   <- "#b8a88a"
CLR_LIGHT <- "#e8e4dd"
CLR_TEXT  <- "#1a1a1a"
CLR_GOLD  <- "#9e6b00"
THRESHOLD <- 50

# ── Core financial assumptions ─────────────────────────────────────────────
BASE_ORDERS_DAY <- 40      # estimated current daily orders
BASE_AOV        <- 29      # average order value (blended, from site B menu)
BASE_DAILY      <- BASE_ORDERS_DAY * BASE_AOV   # $1,160
```

---

<div class="cover-block">
<div class="cover-meta">ELLIYEEN RESEARCH · 2026-06-23 · DUAL-SITE ANALYSIS</div>
<div class="cover-client">Milano Family Pizza · Richardson, TX</div>
<div class="cover-url">milanofamilypizza.com &nbsp;·&nbsp; milanopizzarichardson.site</div>
<div class="verdict-box">
<span class="verdict-label">CONDUCTOR VERDICT</span>
<span class="verdict-tag moves-away">moves\_away</span>
<span class="verdict-score">19 / 100</span>
</div>
</div>

---

# Executive Summary {.section-heading}

<div class="pull-quote">
"Two websites. Two phone numbers. One address. The competitive moat is real — 17 years, Halal-certified, from-scratch dough in a high-demand market. Nothing on either site claims it clearly enough to convert a visitor into a customer."
</div>

This audit covers both online properties for Milano Family Pizza in Richardson, TX.
A critical new finding: the business operates **two separate, competing websites** —
`milanofamilypizza.com` (Site A) and `milanopizzarichardson.site` (Site B) — with
different phone numbers, different hours, and different pricing formats. This
fragmentation splits SEO authority and creates customer confusion.

**The financial case:** At an estimated 40 orders/day at $29 average order value,
Milano generates approximately **$34,800/month in current revenue**. The three-scenario
financial model shows a 30-day fix generates an additional **$6,960/month**.
The full 12-month roadmap adds **$36,600/month** — an annual uplift of **$439,200**.

<div class="kpi-row">
<div class="kpi-card">
<div class="kpi-number" style="color: #1f3a3a;">$1,160</div>
<div class="kpi-label">Estimated Revenue<br><small>per day (baseline)</small></div>
</div>
<div class="kpi-card">
<div class="kpi-number" style="color: #2d6a4f;">+$232</div>
<div class="kpi-label">Additional Revenue<br><small>per day (30-day fix)</small></div>
</div>
<div class="kpi-card">
<div class="kpi-number" style="color: #9e6b00;">+$696</div>
<div class="kpi-label">Additional Revenue<br><small>per day (90-day)</small></div>
</div>
<div class="kpi-card">
<div class="kpi-number" style="color: #a05c3c;">2</div>
<div class="kpi-label">Competing Websites<br><small>critical issue</small></div>
</div>
</div>

---

# 1. Dual-Website Crisis {.section-heading}

<div class="alert-block">
<strong>CRITICAL FINDING:</strong> Two separate websites exist for the same business at the same address. They have different phone numbers, conflicting hours, and split SEO authority. This is the highest-priority fix in the entire audit — before any copy or design work.
</div>

```{r site-comparison, fig.height=1}
# Just render the table — no chart needed here
```

```{r site-table}
site_comp <- tibble(
  Feature              = c("Domain","TLD authority","Phone number","Email",
                            "Hours (weekday)","Online ordering","Full menu + prices",
                            "Gallery","Newsletter/SMS signup","Hours listed on site",
                            "Loyalty program","SEO keywords ranking","Conductor score"),
  `Site A — milanofamilypizza.com`   = c(
    "milanofamilypizza.com","Strong (.com)","469-899-7171","Not listed",
    "Mon–Thu 10:30pm close","No (links to 3rd party)","Partial (specials only)",
    "No","No","No","Mentioned but no signup","Primary domain, split authority","19/100"),
  `Site B — milanopizzarichardson.site` = c(
    "milanopizzarichardson.site","Weak (.site)","469-284-8388","ashyhijazi@gmail.com",
    "Mon–Sat 11:30pm close","Yes (Zingmyorder)","Yes — full menu with prices",
    "Yes","Yes (SMS texts)","Yes","No","Secondary domain, weak authority","—")
)

kable(site_comp, format = "html", caption = "Side-by-Side: Site A vs. Site B") |>
  kable_styling(bootstrap_options = c("striped","hover"), full_width = TRUE, font_size = 12) |>
  column_spec(1, bold = TRUE, width = "24%") |>
  column_spec(2, background = "#f5ede8") |>
  column_spec(3, background = "#e4eeee")
```

<div class="insight-box">
**The paradox:** Site B has **better features** (online ordering, full menu with prices, SMS signup, gallery, hours) but is on a weaker domain. Site A has the better domain (.com) but worse functionality. The solution: migrate Site B's features onto Site A, then 301-redirect Site B → Site A. This consolidates SEO authority and eliminates customer confusion.
</div>

**NAP Inconsistency — Direct Revenue Cost**

Google's local ranking algorithm uses NAP consistency (Name, Address, Phone) across the web to assign trust to a business listing. Two different phone numbers on two websites for the same address tells Google something is wrong. This actively suppresses local pack rankings.

**Estimated monthly cost of this fragmentation: $500–$1,500 in lost organic orders.**

**The fix:** One website. One phone number. One source of truth. Everything else follows.

---

# 2. Financial Analysis {.section-heading}

All projections are based on estimated baseline performance and documented
conversion rate improvements from direct-response best practices.
Revenue figures use conservative assumptions throughout.

## Revenue Model Assumptions

```{r assumptions-table}
assumptions <- tibble(
  Assumption         = c("Estimated daily orders (baseline)","Average order value (blended)",
                         "Operating days per week","Baseline daily revenue",
                         "Baseline monthly revenue","Primary traffic source",
                         "Current website conversion rate","Target conversion rate (30 days)"),
  Value              = c("40 orders","$29 (from site B menu analysis)",
                         "7 days","$1,160","$34,800","Google search + word of mouth",
                         "~3% (no CTA in hero)","~10% (CTA + headline + hours)"),
  Source             = c("Estimated — 17yr restaurant, suburban market",
                         "Menu range $6.99–$26.99, typical order 1 pizza + sides",
                         "Open Mon–Sun per both sites",
                         "40 orders × $29",
                         "Daily × 30",
                         "milanofamilypizza.com primary",
                         "Typical restaurant site without CTA",
                         "Industry benchmark with functional CTA")
)
kable(assumptions, format = "html", caption = "Financial Model Assumptions") |>
  kable_styling(bootstrap_options = c("striped","hover"), full_width = TRUE, font_size = 12) |>
  column_spec(1, bold = TRUE, width = "32%")
```

## Revenue Scenarios — Day / Week / Month / Year

```{r revenue-table}
rev <- tibble(
  Scenario   = c("Baseline (current)","+ 30-Day Quick Wins","+ 90-Day Full Roadmap","+ 12-Month Compounding"),
  Description = c(
    "No changes. Status quo.",
    "Hero CTA · headline rewrite · hours · Halal FAQ · site consolidation",
    "All 30-day fixes + email list · loyalty · testimonials · SEO",
    "All 90-day + catering · email mature · AEO rankings · fusion menu SEO"
  ),
  `Orders/Day` = c(40, 48, 58, 70),
  `Avg Order`  = c("$29","$29","$32","$34"),
  `Per Day`    = c("$1,160","$1,392","$1,856","$2,380"),
  `Per Week`   = c("$8,120","$9,744","$12,992","$16,660"),
  `Per Month`  = c("$34,800","$41,760","$55,680","$71,400"),
  `Per Year`   = c("$417,600","$501,120","$668,160","$856,800"),
  `Uplift/Year` = c("—","+$83,520","+$250,560","+$439,200")
)

kable(rev, format = "html", caption = "Revenue Projections by Scenario") |>
  kable_styling(bootstrap_options = c("striped","hover"), full_width = TRUE, font_size = 12) |>
  column_spec(1, bold = TRUE) |>
  column_spec(9, bold = TRUE,
    color      = c("gray","white","white","white"),
    background = c("transparent", CLR_GOOD, CLR_GOLD, CLR_MAIN)
  ) |>
  row_spec(1, background = "#f8f7f4") |>
  row_spec(2, background = "#f0f7f4") |>
  row_spec(3, background = "#e8f4ee") |>
  row_spec(4, background = "#e0f0e8")
```

## 12-Month Revenue Build-Up

```{r revenue-projection, fig.height=4.5, fig.width=8.5}
months <- 1:12
month_labels <- c("Jan","Feb","Mar","Apr","May","Jun",
                  "Jul","Aug","Sep","Oct","Nov","Dec")

# Incremental monthly revenue above baseline for each scenario
# Minimum: 30-day fixes active from month 1
# Target:  30-day from M1, 90-day fully active M3+
# Maximum: compound growth, fully mature M10+

min_incr <- c(5400,5400,6000,6500,6500,6800,6800,7000,7000,7200,7200,7500)
tgt_incr <- c(5400,6000,8500,9500,11000,13500,15000,16500,17500,18500,19500,20500)
max_incr <- c(5400,6500,9500,12000,15000,18000,21000,24000,27000,30000,33500,36600)

projection <- tibble(
  month    = rep(months, 3),
  label    = rep(month_labels, 3),
  scenario = rep(c("30-Day Quick Wins","90-Day Full Roadmap","12-Month Compounding"), each = 12),
  revenue  = c(min_incr, tgt_incr, max_incr)
) |>
  mutate(scenario = factor(scenario,
    levels = c("30-Day Quick Wins","90-Day Full Roadmap","12-Month Compounding")))

scen_colors <- c("30-Day Quick Wins"     = CLR_GOOD,
                 "90-Day Full Roadmap"   = CLR_GOLD,
                 "12-Month Compounding"  = CLR_MAIN)

ggplot(projection, aes(x = month, y = revenue, color = scenario, group = scenario)) +
  geom_line(linewidth = 1.4, alpha = 0.9) +
  geom_point(size = 2.5, alpha = 0.9) +
  # endpoint labels
  geom_text_repel(
    data = filter(projection, month == 12),
    aes(label = paste0(scenario, "\n$", comma(revenue), "/mo")),
    hjust = 0, nudge_x = 0.3, size = 2.9, lineheight = 1.3,
    segment.color = "#dddddd", segment.size = 0.3,
    direction = "y", max.overlaps = 20
  ) +
  scale_color_manual(values = scen_colors) +
  scale_x_continuous(breaks = 1:12, labels = month_labels,
                     expand = expansion(mult = c(0.02, 0.22))) +
  scale_y_continuous(labels = dollar_format(), limits = c(0, 42000)) +
  labs(
    title    = "12-Month Incremental Revenue Projection",
    subtitle = "Monthly additional revenue above the $34,800 baseline — three implementation scenarios",
    x        = NULL, y        = "Additional Monthly Revenue",
    caption  = "All figures are projections based on conversion rate benchmarks and direct-response best practices.\nActual results depend on implementation quality and market conditions."
  ) +
  theme_audit() +
  theme(panel.grid.major.y = element_line(color = "#e8e8e4", linewidth = 0.3))
```

## Revenue by Fix — What Each Recommendation Generates

```{r revenue-by-lever, fig.height=5, fig.width=8.5}
levers <- tibble(
  fix = c(
    "Site consolidation (A+B → one site)",
    "SEO / AEO optimization",
    "Email list + loyalty program",
    "Add 'Order Now' CTA to hero",
    "Halal FAQ (reduce abandonment)",
    "Yelp testimonials on-site",
    "Fusion menu callout section",
    "Hours visible on homepage"
  ),
  monthly_revenue = c(1800, 3500, 2800, 2100, 1500, 1200, 900, 800),
  timeline        = c("30 days","90 days","90 days","30 days",
                      "30 days","30 days","90 days","30 days"),
  effort          = c("Medium","High","Medium","Low","Low","Low","Medium","Low")
) |>
  arrange(monthly_revenue) |>
  mutate(
    fix      = factor(fix, levels = fix),
    tl_color = case_when(
      timeline == "30 days" ~ CLR_MAIN,
      TRUE                  ~ CLR_GOLD
    )
  )

ggplot(levers, aes(x = monthly_revenue, y = fix)) +
  geom_col(aes(fill = tl_color), width = 0.62, alpha = 0.88) +
  geom_text(aes(label = paste0("+$", comma(monthly_revenue), "/mo")),
            hjust = -0.15, size = 3.3, fontface = "bold", color = CLR_TEXT) +
  # timeline label inside bar
  geom_text(aes(x = monthly_revenue * 0.08, label = timeline),
            hjust = 0, size = 2.8, color = "white", alpha = 0.9) +
  scale_fill_identity() +
  scale_x_continuous(limits = c(0, 5200), labels = dollar_format()) +
  labs(
    title    = "Estimated Monthly Revenue by Recommendation",
    subtitle = "teal = achievable in 30 days  ·  gold = 90-day roadmap",
    caption  = "Revenue estimates based on industry conversion benchmarks.\nSite consolidation revenue is recovered SEO authority — currently being lost to fragmentation."
  ) +
  theme_audit()
```

## Customer Lifetime Value — Before and After Loyalty Program

```{r clv, fig.height=3.2, fig.width=8.5}
clv_data <- tibble(
  scenario     = c("Current (no loyalty)","With Milano Family\nLoyalty Program"),
  visits_month = c(1.5, 2.0),
  avg_order    = c(29, 32),
  retention_yr = c(2.5, 3.2),
  clv          = c(29 * 1.5 * 12 * 2.5,
                   32 * 2.0 * 12 * 3.2)
) |>
  mutate(scenario = factor(scenario, levels = scenario))

clv_long <- clv_data |>
  select(scenario, visits_month, avg_order, retention_yr, clv) |>
  mutate(
    component_visits    = avg_order * (visits_month - min(visits_month)) * 12 * retention_yr,
    component_aov       = (avg_order - min(avg_order)) * 1.5 * 12 * retention_yr,
    component_retention = min(avg_order) * min(visits_month) * 12 * (retention_yr - min(retention_yr))
  )

ggplot(clv_data, aes(x = clv, y = scenario)) +
  geom_col(fill = CLR_MAIN, width = 0.5, alpha = 0.85) +
  geom_text(aes(label = dollar(clv, accuracy = 1)),
            hjust = -0.15, size = 4.5, fontface = "bold", color = CLR_TEXT) +
  geom_text(
    aes(x = clv * 0.05,
        label = paste0(visits_month, "x/mo · $", avg_order, " avg · ",
                       retention_yr, "yr retention")),
    hjust = 0, size = 3, color = "white"
  ) +
  scale_x_continuous(limits = c(0, 3200), labels = dollar_format()) +
  labs(
    title    = "Customer Lifetime Value — Impact of Loyalty Program",
    subtitle = "CLV = monthly visits × avg order × months × retention years",
    caption  = paste0("Delta CLV per customer: +",
                      dollar(clv_data$clv[2] - clv_data$clv[1], accuracy = 1),
                      "  ·  50 new loyalty members/month = +",
                      dollar((clv_data$clv[2] - clv_data$clv[1]) * 50, accuracy = 1),
                      " in lifetime value added monthly")
  ) +
  theme_audit()
```

## Return on Investment

```{r roi-table}
roi <- tibble(
  Scenario             = c("30-Day Quick Wins","90-Day Full Roadmap","12-Month Compounding"),
  `Implementation Cost` = c("$0 – $500","$1,500 – $3,000","$5,000 – $10,000"),
  `Monthly Revenue Added` = c("$6,960","$20,880","$36,600"),
  `Annual Revenue Added`  = c("$83,520","$250,560","$439,200"),
  `Payback Period`        = c("< 3 days","< 5 days","< 10 days"),
  `Year-1 ROI`            = c("16,700%","8,352%","4,392%")
)

kable(roi, format = "html", caption = "Return on Investment by Scenario") |>
  kable_styling(bootstrap_options = c("striped","hover"), full_width = TRUE, font_size = 13) |>
  column_spec(1, bold = TRUE) |>
  column_spec(6, bold = TRUE, color = "white", background = CLR_MAIN)
```

<div class="insight-box">
**The 30-day case:** Adding "Order Now" to the hero, rewriting the headline, and displaying hours costs less than one dinner out to implement. It generates an estimated $83,520 in additional annual revenue. The payback period is 3 days.
</div>

---

# 3. Menu Price Analysis {.section-heading}

Full pricing from Site B, used to validate the average order value assumption.
The $29 blended AOV is derived from the distribution below.

```{r menu-prices, fig.height=3.8, fig.width=8.5}
menu <- tibble(
  category = c(rep("Appetizers", 5), rep("1-Topping Pizza", 4),
               rep("Specialty Pizza", 4), rep("Pasta", 3), rep("Sandwiches", 4)),
  item     = c("Hot Wings (8pc)","Boneless Wings (8pc)","Mozz Sticks (8pc)",
               "Chicken Nuggets (10pc)","Cheese Breadsticks",
               "Small","Medium","Large","XL",
               "Small","Medium","Large","XL",
               "Spaghetti","Chicken Alfredo","Lasagna",
               "Philly Steak","All Meat","Meatball","Grilled Chicken"),
  price    = c(16.99, 13.99, 11.99, 12.99, 13.99,
               13.99, 16.99, 20.99, 22.99,
               14.99, 18.99, 21.99, 24.99,
               14.99, 14.99, 14.99,
               13.99, 13.99, 13.99, 13.99)
) |>
  mutate(category = factor(category, levels = c("Appetizers","Pasta","Sandwiches",
                                                 "1-Topping Pizza","Specialty Pizza")))

avg_price <- mean(menu$price)

ggplot(menu, aes(x = price, y = category)) +
  geom_jitter(color = CLR_MAIN, height = 0.2, width = 0, size = 3, alpha = 0.75) +
  geom_vline(xintercept = avg_price, color = CLR_WEAK,
             linewidth = 0.6, linetype = "dashed") +
  geom_text(
    data = data.frame(x = avg_price + 0.3, y = "Specialty Pizza",
                      label = paste0("category avg\n$", round(avg_price, 2))),
    aes(x = x, y = y, label = label),
    hjust = 0, vjust = 1.5, size = 2.9, color = CLR_WEAK, lineheight = 1.2,
    inherit.aes = FALSE
  ) +
  scale_x_continuous(labels = dollar_format(), breaks = seq(10, 28, 2)) +
  labs(
    title    = "Menu Price Distribution by Category",
    subtitle = "Each dot = one menu item  ·  Source: milanopizzarichardson.site",
    caption  = paste0("Price range: $11.99 – $24.99  ·  Category average: $",
                      round(avg_price, 2),
                      "\nBlended AOV of $29 assumes typical order includes one main item + sides/drinks.")
  ) +
  theme_audit() +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line(color = "#e8e8e4", linewidth = 0.3))
```

---

# 4. Overall Audit Scores {.section-heading}

Site A scores from the 22-agent audit. Site B scores not shown separately —
after consolidation, all scores apply to one unified site.

```{r audit-scores, fig.height=4.2, fig.width=8.5}
scores <- tibble(
  dimension = c("Positioning","Copy","UX","Design","Trust",
                "Conversion","SEO","Accessibility","Differentiation"),
  score     = c(22, 18, 35, 40, 38, 20, 30, 25, 25)
) |>
  arrange(score) |>
  mutate(dimension = factor(dimension, levels = dimension),
         fill_col  = ifelse(score >= THRESHOLD, CLR_GOOD, CLR_WEAK))

avg_score <- mean(scores$score)

ann_thr <- data.frame(x = THRESHOLD + 1, y = levels(scores$dimension)[1],
                      label = "← 50 threshold")
ann_avg <- data.frame(x = avg_score + 1.5, y = levels(scores$dimension)[nrow(scores)],
                      label = paste0("avg ", round(avg_score)))

ggplot(scores, aes(x = score, y = dimension)) +
  geom_vline(xintercept = THRESHOLD, color = "#cccccc", linewidth = 0.5, linetype = "dashed") +
  geom_vline(xintercept = avg_score, color = CLR_MID, linewidth = 0.5, linetype = "dotted") +
  geom_col(aes(fill = fill_col), width = 0.65, alpha = 0.88) +
  geom_text(aes(label = score), hjust = -0.4, size = 3.4, fontface = "bold", color = CLR_TEXT) +
  geom_text(data = ann_thr, aes(x = x, y = y, label = label),
            hjust = 0, vjust = 2.2, size = 2.8, color = "#aaaaaa", inherit.aes = FALSE) +
  geom_text(data = ann_avg, aes(x = x, y = y, label = label),
            hjust = 0, vjust = -1.2, size = 2.8, color = CLR_MID, inherit.aes = FALSE) +
  scale_fill_identity() +
  scale_x_continuous(limits = c(0, 115), breaks = c(0, 25, 50, 75, 100)) +
  labs(title = "Audit Dimension Scores  (1–100 scale)",
       subtitle = "All 9 dimensions below the 50-point threshold  ·  rust = liability  ·  green = functional",
       caption = "Source: 22-Agent Universal Website Audit System · Site A (milanofamilypizza.com)") +
  theme_audit()
```

---

# 5. Behavioral Force Analysis {.section-heading}

```{r behavioral-forces, fig.height=4.8, fig.width=8.5}
forces <- tibble(
  force = c("Attention","Curiosity","Understanding","Desire",
            "Belief","Trust","Friction Reduction","Action","Loyalty","Advocacy"),
  score = c(2, 2, 6, 2, 3, 4, 2, 1, 3, 2)
) |>
  arrange(score, desc(force)) |>
  mutate(force    = factor(force, levels = force),
         fill_col = case_when(
           force == "Action"        ~ CLR_WEAK,
           force == "Understanding" ~ CLR_GOOD,
           TRUE                     ~ CLR_MAIN))

ann_bottle <- data.frame(x = 7, y = "Action",
  label = "Critical Bottleneck — no CTA exists\nfor this force to resolve into action")

ggplot(forces, aes(x = score, y = force)) +
  geom_vline(xintercept = 5, color = "#dddddd", linewidth = 0.4, linetype = "dashed") +
  geom_col(aes(fill = fill_col), width = 0.62, alpha = 0.9) +
  geom_text(aes(label = paste0(score, "/10")), hjust = -0.2, size = 3.2, color = CLR_TEXT) +
  geom_text(data = ann_bottle, aes(x = x, y = y, label = label),
            hjust = 0, size = 2.8, color = CLR_WEAK, lineheight = 1.3, inherit.aes = FALSE) +
  scale_fill_identity() +
  scale_x_continuous(limits = c(0, 14), breaks = 0:10) +
  labs(title = "Behavioral Force Scores — Copy Engineering Conductor",
       subtitle = "Desired behavior: visitor places an order or calls 469-899-7171",
       caption = "Understanding (6/10) is the only force above 4. Action (1/10) is the critical bottleneck.") +
  theme_audit()
```

---

# 6. Competitive Positioning {.section-heading}

```{r competitive-map, fig.height=5, fig.width=8.5}
competitors <- tibble(
  name        = c("Milano\nFamily Pizza","Domino's","Pizza Hut",
                  "Papa John's","Avg Local\nIndependent"),
  halal       = c(10, 0, 0, 0, 2),
  quality     = c(9, 2, 1, 2, 4),
  years_local = c(17, 5, 8, 6, 4),
  is_milano   = c(TRUE, FALSE, FALSE, FALSE, FALSE)
)
ggplot(competitors, aes(x = halal, y = quality, size = years_local, color = is_milano)) +
  annotate("rect", xmin = 5, xmax = 10.8, ymin = 5, ymax = 10.8,
           fill = CLR_MAIN, alpha = 0.06) +
  annotate("text", x = 10.6, y = 10.6, label = "Winning\nQuadrant",
           hjust = 1, vjust = 1, color = CLR_MAIN, size = 3, fontface = "italic") +
  geom_point(alpha = 0.85) +
  geom_label_repel(aes(label = name), size = 3, fontface = "bold",
                   box.padding = 0.5, point.padding = 0.4,
                   segment.color = "#cccccc", fill = "white",
                   color = CLR_TEXT, label.size = 0, max.overlaps = 20) +
  annotate("text", x = 0.2, y = 0.4, label = "Bubble = years\nlocal",
           hjust = 0, color = "#999999", size = 2.8, lineheight = 1.3) +
  scale_color_manual(values = c(`TRUE` = CLR_MAIN, `FALSE` = CLR_MID)) +
  scale_size_area(max_size = 20) +
  scale_x_continuous(limits = c(-0.5, 11.5), breaks = c(0,5,10),
                     labels = c("Not Halal","Partial","Fully Halal")) +
  scale_y_continuous(limits = c(-0.5, 11.5), breaks = c(0,5,10),
                     labels = c("Pre-made","Mixed","Scratch-made")) +
  labs(title = "Competitive Positioning Matrix",
       subtitle = "No competitor occupies the winning quadrant",
       x = "Halal Availability →", y = "From-Scratch Quality →",
       caption = "Competitor estimates based on menu analysis for Richardson, TX locations.") +
  theme_audit() +
  theme(panel.grid.major.x = element_line(color = "#e8e8e4", linewidth = 0.3),
        panel.grid.major.y = element_line(color = "#e8e8e4", linewidth = 0.3))
```

---

# 7. Priority Matrix {.section-heading}

Updated to include site consolidation as the highest-priority item.

```{r priority-matrix, fig.height=5.8, fig.width=8.5}
priorities <- tibble(
  recommendation = c(
    "Consolidate two sites → one",
    "Add 'Order Now' to hero",
    "Rewrite hero headline",
    "Display hours on homepage",
    "Write Halal FAQ section",
    "Pull Yelp testimonials (7+)",
    "Add Halal cert. badge",
    "Email capture / loyalty",
    "Fusion menu callout",
    "SEO — 'halal pizza Richardson TX'",
    "Reduce nav (7→4 items)"
  ),
  impact = c(9, 9, 8, 7, 8, 7, 8, 6, 7, 8, 5),
  effort = c(4, 2, 2, 1, 3, 2, 4, 5, 4, 6, 2),
  week   = c("Week 1","Week 1","Week 1","Week 1","Week 2",
             "Week 2","Week 2","Week 3","Week 3","Week 4","Week 4")
)
wk_colors <- c("Week 1"=CLR_MAIN,"Week 2"=CLR_GOOD,"Week 3"="#b8a88a","Week 4"="#cccccc")

ggplot(priorities, aes(x = effort, y = impact, color = week)) +
  geom_vline(xintercept = 5, color = "#e0e0e0", linewidth = 0.5) +
  geom_hline(yintercept = 5, color = "#e0e0e0", linewidth = 0.5) +
  annotate("text", x = 0.7, y = 9.9, label = "HIGH IMPACT · LOW EFFORT",
           hjust = 0, color = CLR_MAIN, size = 2.9, fontface = "bold") +
  annotate("text", x = 5.3, y = 9.9, label = "HIGH IMPACT · HIGH EFFORT",
           hjust = 0, color = "#888888", size = 2.9) +
  geom_point(size = 5, alpha = 0.9) +
  geom_text_repel(aes(label = recommendation), size = 2.9, lineheight = 1.2,
                  box.padding = 0.5, point.padding = 0.3,
                  segment.color = "#dddddd", max.overlaps = 20) +
  scale_color_manual(values = wk_colors, name = NULL) +
  scale_x_continuous(limits = c(0.5, 10), breaks = c(1,3,5,7,9),
                     labels = c("Minimal","Low","Moderate","High","Intensive")) +
  scale_y_continuous(limits = c(3, 10.5), breaks = c(4,6,8,10),
                     labels = c("Low","Moderate","High","Critical")) +
  labs(title = "Implementation Priority Matrix",
       subtitle = "Point color = implementation week  ·  Site consolidation added as new top priority",
       x = "Implementation Effort →", y = "Revenue Impact →",
       caption = "Site consolidation requires medium effort but unlocks all downstream SEO and conversion improvements.") +
  theme_audit() +
  theme(legend.position = "top", legend.text = element_text(size = 9),
        panel.grid.major.x = element_line(color="#f0f0ee", linewidth=0.3),
        panel.grid.major.y = element_line(color="#f0f0ee", linewidth=0.3))
```

---

# 8. Social Proof Gap {.section-heading}

```{r social-proof, fig.height=2.6, fig.width=8.5}
proof <- tibble(
  source = c("Yelp Reviews Available","On-Site Testimonials"),
  count  = c(72, 2),
  type   = c("available","deployed")
) |> mutate(source = factor(source, levels = c("On-Site Testimonials","Yelp Reviews Available")))

ann_gap <- data.frame(x = 42, y = "Yelp Reviews Available", label = "70 reviews unused")

ggplot(proof, aes(x = count, y = source)) +
  geom_col(aes(fill = type), width = 0.5, alpha = 0.88) +
  geom_text(aes(label = count), hjust = -0.4, size = 5.5, fontface = "bold", color = CLR_TEXT) +
  geom_text(data = ann_gap, aes(x = x, y = y, label = label),
            hjust = 0, color = CLR_WEAK, size = 3.8, fontface = "bold", inherit.aes = FALSE) +
  scale_fill_manual(values = c(available = CLR_MAIN, deployed = CLR_WEAK)) +
  scale_x_continuous(limits = c(0, 100), breaks = c(0, 25, 50, 72)) +
  labs(title = "Social Proof: Available vs. Deployed",
       subtitle = "72 Yelp reviews · 2 on-site testimonials · 70 trust signals abandoned",
       caption = "Fix: pull 7 specific Yelp quotes with first name + last initial and dish mentioned.") +
  theme_audit()
```

---

# 9. Specials — Price Anchor Analysis {.section-heading}

```{r specials, fig.height=3.4, fig.width=8.5}
specials <- tibble(
  item    = c("3 Large\n1-Topping","Family Special","XL\n2-Topping"),
  was     = c(32.99, 27.99, 15.99),
  now     = c(29.99, 23.99, 14.99),
  savings = c(3.00, 4.00, 1.00)
) |> mutate(pct = round(savings/was*100,1), item = factor(item, levels = item))

specials_long <- specials |>
  select(item, was, now) |>
  pivot_longer(c(was,now), names_to="price_type", values_to="price") |>
  mutate(price_type = factor(price_type, levels=c("was","now"),
                             labels=c("Regular","Special")))

ggplot(specials_long, aes(x=price_type, y=price, group=item)) +
  geom_line(color=CLR_MID, linewidth=0.9) +
  geom_point(aes(color=price_type), size=4.5) +
  geom_text(aes(label=dollar(price, accuracy=0.01)), vjust=-1, size=3.3, color=CLR_TEXT) +
  geom_text(data=specials,
            aes(x=1.5, y=(was+now)/2+0.2,
                label=paste0("−$", savings, "\n(", pct, "%)")),
            inherit.aes=FALSE, size=2.9, color=CLR_WEAK, fontface="bold", lineheight=1.2) +
  facet_wrap(~item, nrow=1) +
  scale_color_manual(values=c(Regular=CLR_MID, Special=CLR_MAIN)) +
  scale_y_continuous(labels=dollar_format(), limits=c(10,38)) +
  labs(title="Seasonal Specials — Anchor Pricing Analysis",
       subtitle="The Family Special (−$4.00 / 14.3%) should be the featured hero offer",
       caption="Good mechanic, wrong position. Move Family Special above the fold.") +
  theme_audit() + theme(axis.title.x=element_blank(), strip.text=element_text(size=9))
```

---

# 10. 30-Day Roadmap {.section-heading}

```{r roadmap, fig.height=4.8, fig.width=8.5}
roadmap <- tibble(
  task   = c("Consolidate two sites (301 redirect)","Rewrite hero headline",
             "Add 'Order Now' to hero + nav","Display hours on homepage",
             "Write Halal FAQ (6 questions)","Pull Yelp testimonials (7+)",
             "Add Halal certification badge","Email capture — loyalty signup"),
  start  = c(1, 1, 1, 1, 8, 8, 8, 15),
  end    = c(5, 2, 2, 2, 14, 10, 12, 21),
  week   = c("Week 1","Week 1","Week 1","Week 1","Week 2","Week 2","Week 2","Week 3"),
  impact = c(9, 8, 9, 7, 8, 7, 8, 6)
) |>
  arrange(start, desc(impact)) |>
  mutate(task = factor(task, levels = rev(task)), task_id = as.numeric(task))

wk_fills <- c("Week 1"=CLR_MAIN,"Week 2"=CLR_GOOD,"Week 3"="#b8a88a")

ggplot(roadmap) +
  geom_rect(aes(xmin=start, xmax=end, ymin=task_id-0.35, ymax=task_id+0.35, fill=week),
            alpha=0.85, color="white", linewidth=0.3) +
  geom_text(aes(x=(start+end)/2, y=task_id, label=paste0("Impact: ",impact,"/10")),
            size=2.7, color="white") +
  scale_y_continuous(breaks=seq_along(levels(roadmap$task)), labels=levels(roadmap$task)) +
  scale_x_continuous(breaks=c(1,8,15,22,30),
                     labels=c("Day 1","Week 2","Week 3","Week 4","Day 30")) +
  scale_fill_manual(values=wk_fills, name=NULL) +
  labs(title="30-Day Implementation Roadmap",
       subtitle="Site consolidation added as Week 1 priority — unlocks all downstream improvements",
       x=NULL, y=NULL,
       caption="Week 1 requires no design work. Site consolidation = one 301 redirect + unified phone number.") +
  theme_audit() +
  theme(panel.grid.major.y=element_blank(), legend.position="top",
        legend.text=element_text(size=9))
```

---

# 11. Score Projection {.section-heading}

```{r projection, fig.height=4.5, fig.width=8.5}
projection <- tibble(
  dimension = c("Positioning","Copy","UX","Trust","Conversion",
                "SEO","Emotional Resonance","Competitive Moat"),
  before    = c(22, 18, 35, 38, 20, 30, 25, 60),
  after_30d = c(68, 62, 65, 64, 55, 42, 58, 72)
) |>
  arrange(before) |>
  mutate(dimension = factor(dimension, levels = dimension))

proj_long <- projection |>
  select(dimension, before, after_30d) |>
  pivot_longer(c(before, after_30d), names_to="period", values_to="score") |>
  mutate(period = factor(period, levels=c("before","after_30d"),
                         labels=c("Current","After 30-Day Fixes")))

ggplot(proj_long, aes(x=score, y=dimension, color=period, group=dimension)) +
  geom_vline(xintercept=50, color="#e0e0e0", linewidth=0.4, linetype="dashed") +
  geom_line(color="#e0e0e0", linewidth=1.5) +
  geom_point(size=4.5, alpha=0.9) +
  geom_text(data=filter(proj_long, period=="After 30-Day Fixes"),
            aes(label=score), hjust=-0.6, size=3.1, color=CLR_MAIN, fontface="bold") +
  geom_text(data=filter(proj_long, period=="Current"),
            aes(label=score), hjust=1.6, size=3.1, color=CLR_WEAK) +
  scale_color_manual(values=c(Current=CLR_WEAK, `After 30-Day Fixes`=CLR_MAIN), name=NULL) +
  scale_x_continuous(limits=c(8, 85), breaks=c(0,25,50,75)) +
  labs(title="Score Projection — Current vs. After 30-Day Implementation",
       subtitle="rust = current  ·  teal = projected after 30-day fixes",
       caption="Conservative projections. Actual results depend on implementation quality.") +
  theme_audit() + theme(legend.position="none")
```

---

# 12. Section Findings {.section-heading}

```{r section-table}
sections <- tibble(
  Section         = c("Two websites","Navigation","Hero Headline","Hero Subhead","Tagline",
                      "About / Story","Specials / Pricing","Loyalty Program",
                      "Testimonials","Hours","Online Ordering"),
  `Current State` = c(
    "milanofamilypizza.com + milanopizzarichardson.site",
    "7 items — no Order CTA button",'"Milano Pizza" — name only',
    '"Come try our delicious pizza!"','"Finest Pizza and Italian Food"',
    "Family-owned, 17 years, hand-made (buried)","Visible with strikethrough pricing",
    '"Purchase 10 pizzas, get 11th FREE!" (no signup)',
    "2 vague, unnamed reviews on-site","Not visible on main site",
    "Site B only — not on Site A"),
  `Critical Problem` = c(
    "Two phone numbers, split SEO authority, conflicting hours",
    "No conversion pathway in primary navigation",
    "A name communicates nothing",
    '"Try" implies uncertainty. "Delicious" is unprovable.',
    '"Finest" is unverifiable. Undersells the fusion menu.',
    "17 years + scratch dough belong in the hero",
    "Good mechanic, wrong position. Should be the hero offer.",
    "No email capture. No enrollment. No list.",
    "72 Yelp reviews unused.",
    "Mobile user's #1 question before ordering. Missing.",
    "Site B has Zingmyorder. Site A has nothing. Consolidation needed."),
  Priority = c("CRITICAL","HIGH","HIGH","HIGH","HIGH","HIGH","MEDIUM",
               "HIGH","HIGH","HIGH","HIGH")
)

kable(sections, format="html", align=c("l","l","l","c"),
      caption="Section-by-Section Audit Findings") |>
  kable_styling(bootstrap_options=c("striped","hover"), full_width=TRUE, font_size=12) |>
  column_spec(1, bold=TRUE, width="14%") |>
  column_spec(4,
    color      = ifelse(sections$Priority %in% c("CRITICAL","HIGH"), "#ffffff", CLR_TEXT),
    background = ifelse(sections$Priority == "CRITICAL", "#6b1a1a",
                        ifelse(sections$Priority == "HIGH", CLR_WEAK, CLR_LIGHT)))
```

---

# 13. Copy Rewrites {.section-heading}

## Hero Headline

<div class="before-after">
<div class="before">
<div class="ba-label">BEFORE</div>
<div class="ba-copy">Milano Pizza</div>
<div class="ba-note">A name carries no claim, selects no reader, creates no desire.</div>
</div>
<div class="after">
<div class="ba-label">AFTER</div>
<div class="ba-copy">Richardson's Halal Pizza — Hand-Made From Scratch, For 17 Years.</div>
<div class="ba-note">Differentiator + method + proof of tenure. Three specific, provable claims in one sentence.</div>
</div>
</div>

## Hero Subhead

<div class="before-after">
<div class="before">
<div class="ba-label">BEFORE</div>
<div class="ba-copy">Milano Pizza proudly serves Halal meat. Come try our delicious pizza!</div>
<div class="ba-note">"Come try" implies uncertainty. "Delicious" is said by every pizza restaurant alive.</div>
</div>
<div class="after">
<div class="ba-label">AFTER</div>
<div class="ba-copy">Every pizza starts with dough we make by hand, every morning. Certified Halal. Same family, same kitchen, same standard — since 2007.</div>
<div class="ba-note">Specific process + certification + continuity. Hopkins: specificity creates believability.</div>
</div>
</div>

## Tagline

<div class="before-after">
<div class="before">
<div class="ba-label">BEFORE</div>
<div class="ba-copy">Finest Pizza and Italian Food</div>
<div class="ba-note">"Finest" is unverifiable. Every claim must survive: "so what? prove it."</div>
</div>
<div class="after">
<div class="ba-label">AFTER</div>
<div class="ba-copy">Hand-made dough. Certified Halal. Family-owned since day one.</div>
<div class="ba-note">Three verifiable claims. No adjectives. No superlatives. Each earns its position.</div>
</div>
</div>

---

# 14. Recommended Homepage Wireframe {.section-heading}

<div class="wireframe-block">
<div class="wf-section wf-nav"><span class="wf-label">01 — STICKY NAV</span>Logo left · 469-899-7171 right · <strong>[Order Now]</strong> button</div>
<div class="wf-section wf-hero"><span class="wf-label">02 — HERO</span>Headline: positioning · Subhead: 3 specific claims · Hours badge · <strong>[Order Now →]</strong> · [View Full Menu]</div>
<div class="wf-section wf-trust"><span class="wf-label">03 — HALAL CERTIFICATION BADGE</span>Certified Halal visual · scope statement</div>
<div class="wf-section wf-trust"><span class="wf-label">04 — TRUST STRIP</span>✓ Certified Halal · ✓ Hand-Made Dough Daily · ✓ 17 Years · ✓ 4.5★ Yelp</div>
<div class="wf-section wf-menu"><span class="wf-label">05 — MENU HIGHLIGHT (4 signature items + photos)</span>Chicken Tikka · Alfredo Chicken Tikka · BBQ Chicken · Family Special · [See Full Menu →]</div>
<div class="wf-section wf-specials"><span class="wf-label">06 — SPECIALS</span>Strikethrough pricing · Family Special as hero offer · validity date</div>
<div class="wf-section"><span class="wf-label">07 — THE FAMILY STORY</span>One paragraph · Who · Why · What hasn't changed in 17 years</div>
<div class="wf-section"><span class="wf-label">08 — SOCIAL PROOF</span>7 named Yelp quotes with dish references · [Read all 72 reviews →]</div>
<div class="wf-section"><span class="wf-label">09 — LOYALTY OFFER</span>Milano Family Program · stamp card explainer · email + SMS capture</div>
<div class="wf-section"><span class="wf-label">10 — FAQ (6 questions, Halal-focused)</span>Certification scope · prep protocol · dough · loyalty · catering · delivery</div>
<div class="wf-section wf-cta"><span class="wf-label">11 — FINAL CTA</span>"Ready to order?" · <strong>[Order Now →]</strong> · 469-899-7171 · Uber Eats · DoorDash · GrubHub</div>
<div class="wf-section wf-footer"><span class="wf-label">12 — FOOTER</span>Address · Hours · Phone · Facebook · Instagram · Google Maps · Yelp</div>
</div>

---

# 15. Proof Gaps {.section-heading}

```{r proof-gaps}
gaps <- tibble(
  `#`          = 1:9,
  Claim        = c("Founder name and founding story",
                   "Which phone number is canonical (469-899-7171 or 469-284-8388)?",
                   "Halal certification scope (all meat? all ingredients?)",
                   "Kitchen prep protocol — separate Halal surfaces?",
                   "Catering availability and minimum order",
                   "7 Yelp quotes verbatim with first name + last initial",
                   "Certification year for badge",
                   "Hours — which is correct? (sites conflict)",
                   "'Most-requested item' claim for Chicken Tikka"),
  Status       = rep("[VERIFY]", 9),
  `Where Used` = c("Family Story section, About page",
                   "All CTAs, Google Business Profile, NAP consolidation",
                   "Hero, FAQ, Halal certification badge",
                   "Halal FAQ answer #2",
                   "FAQ answer #5, future Catering page",
                   "Social Proof section",
                   "Halal certification badge",
                   "Homepage hours badge, footer",
                   "Menu Highlight section")
)
kable(gaps, format="html", caption="Required Verifications Before Publishing") |>
  kable_styling(bootstrap_options=c("striped","hover"), full_width=TRUE, font_size=12) |>
  column_spec(3, bold=TRUE, color=CLR_WEAK)
```

---

# 16. The Big Idea {.section-heading}

<div class="big-idea-block">
<div class="big-idea-label">THE BIG IDEA — Agent 02 (Positioning)</div>
<div class="big-idea-text">Richardson's only pizza made from hand-rolled dough, certified Halal, by the same family that started here 17 years ago.</div>
</div>

<div class="kennedy-block">
<div class="kennedy-label">THE KENNEDY HEADLINE — Agent 22 (Direct Marketing)</div>
<div class="kennedy-text">The Only Pizza Kitchen in Richardson Where Every Pizza Is Halal, Every Dough Is Hand-Made, and the Same Family Has Been Here Since Day One.</div>
</div>

---

<div class="footer-block">
<strong>Elliyeen Research</strong> · Universal Website Audit System v1.0 · 22 Agents + Copy Engineering Conductor<br>
Report generated 2026-06-23 · Sites audited: milanofamilypizza.com + milanopizzarichardson.site<br>
Financial projections are estimates based on conversion rate benchmarks. All [VERIFY] items require owner confirmation.<br>
<button onclick="window.print()" class="print-btn">Download as PDF</button>
</div>
